Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-13 paper/ms.tex
propagate to ms

In systems like LP 12-502, the observed
variability would probably drive one toward a picture of a
disintegrating planetesimal swarm, rather than just a single
planetesimal.  The need for more than just one launching body 
is because we see dips appear and disappear at
many different phases, but with roughly the same period.  The observed
changing dip depths in response to flares would be understood through
the planetesimal outflow rates being stalled by changes in the local
magnetic field or coronal plasma density.  The sizes of these
purported planetesimals would need to be $\lesssim 1$\,$R_\oplus$,
based on the non-detections of their transits, analogous to e.g.
K2-22 \citep{2015ApJ...812..112S} or KOI-2700
\citep{2014ApJ...784...40R}.  Typical sizes of bodies in the asteroid
belt for instance span hundreds of meters to a few kilometers.

>>>>

In systems like LP 12-502, the observed
variability would perhaps drive one toward a picture of a
disintegrating planetesimal swarm, rather than just a single
planetesimal.  The need for more than just one launching body 
is because we see dips appear and disappear at
many different phases, but with roughly the same period.  The observed
changing dip depths in response to flares would be understood through
the planetesimal outflow rates being stalled by changes in the local
magnetic field or coronal plasma density.  The sizes of these
purported planetesimals would need to be $\lesssim 1$\,$R_\oplus$,
based on the non-detections of their transits, analogous to e.g.
K2-22 \citep{2015ApJ...812..112S} or KOI-2700
\citep{2014ApJ...784...40R}.  Typical sizes of bodies in the asteroid
belt for instance span hundreds of meters to a few kilometers.
